### 2018-05-28 msc_diploma_cubesat_galgoczi.tex
aa

The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot)  CubeSats (miniaturized satellites). The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic protons and electrons.

@@

There would most likely be four scintillators on the CAMELOT satellite. On two neighbouring sides of the satellite have two scintillators each. The scintillator will have a case either from aluminium or carbon fibre.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/satellite_modules.png}
\caption{The modules of the satellite}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{Side extensions including of the CAMELOT satellite (left) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right)}
\label{fig:scints}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\label{fig:spectras_meas}
\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out}
\label{fig:spectra}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right}
 \end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=80.0mm]{images/1channelelectronics.png}
\caption{The schematic design of the readout of the MPPC for the 1 channel configuration}
\label{fig:el1ch}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=80.0mm]{images/2channelelectronics.png}
\caption{The schematic design of the readout electronics of the 2 channel setup}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/irradiation.png}
\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image}
\label{fig:this_set}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=130.0mm]{images/2channelsetup.png}
\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator}
\label{fig:schem2c}
\end{figure}

@@

\begin{figure}[h!]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.35\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The CAD model of the satellite (on the right) and the view of the imported model in Geant (on the left)}
 \end{figure}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	100	& 	Aluminum 7075-T73	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite}
\label{table:materials}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline
Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline			
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
\end{tabular}
\end{center}
\caption{The chemical composition of materials in mass fraction that are used for the satellite}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=80.0mm]{images/positions.png}
\caption{The positions of irradiation for the investigation of the response of the scintillator}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\label{fig:sim_res_calib}
\end{figure}

@@

In order to quantify the detection, the number of particles detected was used as a measure. 10.000 $\gamma$ particles were shot at the detector paralelly on an area of 60cm x 60cm from several angles around the longitudinal axis of the satellite. This way the self absorption of the satellite was quantified.

@@

Therefore the total flux from GRB 990123 at peak intensity was 9.866 photons for every $cm^{2}$ each second. The illuminated area in the simulation was 3600 cm$^{2}$. Thus the simulated 10.000 photons correspond to 282 $\mu$s. Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the countnumber for a second.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=130.0mm]{images/gammashittingsat.png}
\label{eq:diffpos}
\caption{The number of detections from the 10.000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
\end{center}
\end{figure}

As one expects the most $\gamma$s ($\sim$ 200) are detected when these particles hit the scintillator directly, with a perpendicular direction to the surface of the satellite. The effective area of the scintillator is the largest in this case and the $\gamma$s are not absorbed by the material of the satellite.

The worst case scenario is then the $\gamma$s hit the satellite with a direction parallel with the plane of the scintillator. Although some detections ($\sim$ 20) occur even in this case because $\gamma$s that scatter in the material of the satellite can be detected. In fig. \ref{fig:diffpos} one can see the number of detections from 10.000 $\gamma$s shot at the detector for a given position of the GRB.

@@

The total flux from the spectrum taken from SPENVIS (fig. \ref{fig:electrs})for 1 s and a cm$^{2}$ was 2.695.370.

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/electronabsorption.png}[H!]
\caption{The ammount of electrons detected from 100.000 shoot in the simulation}
\end{figure}

@@

Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at the altitude of 500km. The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123. The induced signal of these particles was determined. This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.

@@

G\'abor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations. Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated. Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.

@@

>>>>

The main aim of this thesis is to simulate the detection of $\gamma$-rays from GRBs with the Constellation Gamma (Camelot) CubeSat(s) (miniaturized satellites) being developed by C3S LLC, Budapest. The Geant4 simulation described in this paper also predicts the background signal originating from solar and cosmic protons and electrons.

@@

The CAMELOT satellite platform is being developed by C3S LLC, Budapest. There would most likely be four scintillators on the CAMELOT satellite. On two neighbouring sides of the satellite have two scintillators each. The scintillator will have a case either from aluminium or carbon fibre.

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/satellite_modules.png}
\caption{The modules of the satellite (Courtesy of C3S LLC) \cite{drawing}}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/scint_on_sate.png}
\caption{Side extensions including of the CAMELOT satellite (left, Courtesy of C3S LLC) where scintillators are placed and and a wrapped scintillator with the MPPC read out (right) \cite{kento}}
\label{fig:scints}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=130.0mm]{images/histo_for_det.png}
\label{fig:spectras_meas}
\caption{Energy spectra obtained by collecting the signal of 1 million $\gamma$ with the one channel and the two channel read out \cite{kento}}
\label{fig:spectra}
\end{figure}

@@

\begin{figure}[htbp]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetup.png}
 \qquad
 \includegraphics[width=.4\textwidth,origin=c,angle=0]{images/1channelsetupbox.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The scintillator on the left and the cage holding the setup on the right \cite{kento}}
 \end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=80.0mm]{images/1channelelectronics.png}
\caption{The schematic design of the readout of the MPPC for the 1 channel configuration \cite{kento}}
\label{fig:el1ch}
\end{center}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=80.0mm]{images/2channelelectronics.png}
\caption{The schematic design of the readout electronics of the 2 channel setup \cite{kento}}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/irradiation.png}
\caption{The $^{241}$Am $gamma$ source was placed in a collimator system as can be seen on the image \cite{kento}}
\label{fig:this_set}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=130.0mm]{images/2channelsetup.png}
\caption{The MPPCs for the 2 channel readout are positioned symmetrically from the center of the scintillator \cite{kento}}
\label{fig:schem2c}
\end{figure}

@@

\begin{figure}[h!]
 \centering % \begin{center}/\end{center} takes some additional vertical space
 \includegraphics[width=.35\textwidth,origin=c,angle=0]{images/satellite.png}
 \qquad
 \includegraphics[width=.5\textwidth,origin=c,angle=90]{images/cad_sat.png} 
 % "\includegraphics" from the "graphicx" permits to crop (trim+clip)
 % and rotate (angle) and image (and much more)
 \caption{\label{fig:i} The CAD model of the satellite \cite{drawing} (on the right, Courtesy of C3S LLC) and the view of the imported model in Geant (on the left)}
 \end{figure}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|} 
 \hline
 Name of module & mass [g] & Type of material & Mass ratio [\%]\\\hline
 ADCS &	710	& Aluminum 6061-T6 &	50\\
			& & Copper Electric	& 25 \\
			& &  Glass Borosilicate 	& 25\\\hline
COM	& 	90	& 	Stainless Steel 	& 2\\
			& 	& Brass Generic		& 25\\
			& 	& Aluminum 7075-T73		& 40\\
			& 	& FR4 Glass-Epoxy sheet	& 	33\\\hline
EPS	& 	750	& 	FR4 Glass-Epoxy sheet		& 25\\
			& 	& Aluminum 6061-T6		& 75\\\hline
OBC	&	50		& FR4 Glass-Epoxy sheet	& 	100\\\hline
STRU	& 	980		& Aluminum 6061-T6	& 	100\\\hline
SP	& 	570		& Solar Panel	& 	100\\\hline
Payload	& 	100	& 	Aluminum 7075-T73	& 	100\\
 \hline
\end{tabular}
\end{center}
\caption{The mass ratio of materials that are used for the satellite (Courtesy of C3S LLC) \cite{drawing}}
\label{table:materials}

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}{ |c|c|c|c|c|c|c|c|c|c|c|c|c|} 
 \hline
%Material name & El. 1	& El. 1 m.r. & El. 2 & El. 2 m.r. &El.3	& El. 3 m.r. &El. 4	& El. 4 m.r. &El.	5& El. 5 m.r. &El.	6& El. 6 m.r. \\\hline
Material name & &&&&&&&&&&& \\\hline
Aluminum 6061-T6 &	Al & 96.90 &	Mg &	1.20 &	Si &	0.80 &	Fe &	0.70 &	Cu &	0.40 & &\\\hline		
Aluminum 7075-T73 &	Al &	88.60 &	Zn &	6.10 &	Mg &	2.90 &	Cu &	2.00 &	Si &	0.40 & &\\\hline		
%Stainless Steel A2-70  AISI 304 (EN 1.4301) &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	Mn &	2.00 &	Si &	1.00 & &\\\hline		
Stainless Steel &	Fe &	66.50 &	Cr &	20.00 &	Ni &	10.50	&Mn &	2.00 &	Si &	1.00 & &\\\hline		
Copper Electric  &Cu &	100.00 & & & & & & & & & &	\\\hline			
Glass Borosilicate &	Si &	42.10 &	O &	54.80 &	B &	3.10 & & & & & &\\\hline			
FR4 Glass-Epoxy &	Si &	23.39 &	O &	36.02 &	C &	37.04 &	H &	3.55 & & & &\\\hline		
Brass Generic &	Cu &	85.00 &	Zn &	15.00 & & & & & & & &\\\hline						
Solar Panel &	Ge &	38.00 &	Si &	24.00 &	O &	20.00 &	C &	13.00 &	H &	4.00 &	B &	1.00\\\hline
\end{tabular}
\end{center}
\caption{The chemical composition of materials in mass fraction that are used for the satellite (Courtesy of C3S LLC) \cite{drawing}}
\end{table}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=80.0mm]{images/positions.png}
\caption{The positions of irradiation for the investigation of the response of the scintillator  \cite{kento}}
\end{figure}

@@

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/calibration_photon_yield.png}[H!]
\caption{The spectra of 11 million photons taken experimentally \cite{kento} (blue histogram) matched up with the results of the simulation (green histogram) and the Gaussian fitted to the simulated data}
\label{fig:sim_res_calib}
\end{figure}

@@

In order to quantify the detection, the number of particles detected was used as a measure. 10,000 $\gamma$ particles were shot at the detector paralelly on an area of 60cm x 60cm from several angles around the longitudinal axis of the satellite. This way the self absorption of the satellite was quantified.

@@

Therefore the total flux from GRB 990123 at peak intensity was 9,866 photons for every $cm^{2}$ each second. The illuminated area in the simulation was 3600 cm$^{2}$. Thus the simulated 10,000 photons correspond to 282 $\mu$s. Therefore the number of particles detected in the simulation had to be multiplied by 3551.76 to achive the countnumber for a second.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=130.0mm]{images/gammashittingsat.png}
\caption{The number of detections from the 10,000 $\gamma$ shoot in the simulation depending on the position of the GRB with respect to the longitudinal axis of the satellite.}
\label{fig:diffpos}
\end{center}
\end{figure}

As one expects the most $\gamma$s ($\sim$ 200) are detected when these particles hit the scintillator directly, with a perpendicular direction to the surface of the satellite. The effective area of the scintillator is the largest in this case and the $\gamma$s are not absorbed by the material of the satellite. The detection rate would be 6,393,168 $\frac{Hz}{cm^{2}}$ at peak flux.

The worst case scenario is then the $\gamma$s hit the satellite with a direction parallel with the plane of the scintillator. Although some detections ($\sim$ 20) occur even in this case because $\gamma$s that scatter in the material of the satellite can be detected. In fig. $\ref{fig:diffpos}$ one can see the number of detections from 10,000 $\gamma$s shot at the detector for a given position of the GRB.

@@

The total flux from the spectrum taken from SPENVIS (fig. \ref{fig:electrs}) for 1 s and a cm$^{2}$ was 1,226,000. Therefore in order to obtain the count rate, the values obtained for the simulation of 1,000,000 electron with different directions have to be avaraged and multiplied by 1.226 $\cdot$ 3600, which yields 230,478 counts each second.

\begin{figure}[h!]
\includegraphics[width=150.0mm]{images/electronabsorption.png}
\caption{The ammount of electrons detected from 1,000,000 shoot in the simulation}
\end{figure}

@@

Fourthly, the effect of cosmic radiation was invastigated by utilizing the energy spectra of cosmic electrons at the altitude of 500km. The satellite was radiated by these particles in Geant4 in the same positions that were used for the $\gamma$-rays of GRB 9900123. The induced signal of these particles was determined, which is about one order of magnitude lower then the signal of a GRB. This needs to be minimalized as it "competes" with the signal of gamma particles from GRBs.

@@

G\'abor Galg\'oczi would like to thank Bal\'azs \'Ujv\'ari for the fruitful discussions they had on Geant4 simulations. Useful comments on detectors made Dezs\"o Varga's advices on detectors were highly appreciated. The model of the satellite was provided by Tarcai Norbert and Wágner Olivér from C3S LLC. Last but not least the author would like to thank Norbert Werner for the continued contributions to this work.

@@

\bibitem{drawing} Private communication, C3S LLC.

\bibitem{kento} Master thesis, K. Torigoe, N. Werner, Y. Fukazawa, N. Uchida, K. Tanaka, T. Mizuno \& H. Takahashi, School of Science, Hiroshima University,

%\bibitem{kento} Master thesis, K. Torigoe, Norbert Werner, Yasushi Fukazawa, Nagomi Uchida, Koji Tanaka, Tsunefumi Mizuno \& Hiromitsu Takahashi, School of Science, Hiroshima University,
